Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2020-08-21 analysis/paper/paper.Rmd
edit elevation plot

elevation_sp_sub_plot <- 
ggplot(kasv_tidy,
       aes(has_sp, 
           altitude.m._of_main_layer)) +
  geom_boxplot() +
  theme_bw(base_size = 8)  +
  labs(x = "Stemmed points present",
       y = "Elevation")

>>>>

elevation_sp_sub_plot <- 
ggplot(kasv_tidy,
       aes(has_sp, 
           altitude.m._of_main_layer)) +
  geom_boxplot() +
  theme_bw(base_size = 8)  +
  labs(x = "Stemmed points present",
       y = "Elevation above sea level (m)")
